More than Likes: A bla bla of bla bla with bla bla

### 2023-02-20 paper.Rmd
added plots

---
title: 'Assignment 2: Interpreting Quantitative Findings'
subtitle: |
  | 
  | University of Glasgow
  | `r source("scripts/utils.R")`
  | Student ID: 2819052
  | Course: Quantitative Methods
  | Number of words: `r RmdWords("paper.Rmd")$num_words`
output:
  pdf_document:
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: yes
header-includes:
- \usepackage{amsmath}
- \usepackage{booktabs}
- \usepackage{floatrow}
- \floatsetup[figure]{capposition=top}
- \floatsetup[table]{capposition=top}
bibliography: references.bib 
csl: chicago-author-date
link-citations: yes
nocite: '*'
---

@@

# Introduction
<!-- Word count: approx. 400  -->
<!-- Look at the model in part 2 below. Based on this state a research question and a hypothesis. Remember a hypothesis needs at least two variables. -->

In 1998, the Good Friday/Belfast Agreement was signed and later validated by the voters, and this agreement marked a new era of hope towards peace, equality, and inclusion in Northern Ireland [@galligan2013gender]. The main focus on the agreement and referendum was obviously to stop the violent conflict and seek peace, but one part of the agreement also emphasized an equality agenda [@Hayward2021]. Thus, the agreement also marked the first Northern Irish formal recognition of women's rights to political inclusion [@galligan2013gender]. However, a formal recognition does not necessarily imply that gender equality trickles down into social norms and practices. Therefore, this report examines the contemporary state of women's equality in Northern Ireland.

Perhaps, the most central concept within gender equality is the *gender pay gap*. Disparities in income is an important indicator for gender equality, because it has social, economic, and physiological consequences [@bishu2017gender]. Research on this area have identified several factors that seems to influence a gender pay gap. One such factor can be inequality in access to workplace authority, where women are denied manager or supervisor position although there were equally qualified [@bishu2017gender]. Other factors can be discrimination in hiring or promotion processes, but also lack of gender representation can avoid minorities to even apply for a job or promition [@bishu2017gender].

Deductive [@bryman2016social 33]

<!--  \pagebreak -->
# Data and method
<!-- Word count: approx. 800 -->
<!-- In this section your goal is to demonstrate that you can describe data and that you understand research design and data collection. -->

We employ a cross-sectional design [@bryman2016social 53]

## Sample and Data Collection

Two-tailed t-test [fogarty2018quantitative 156]
Chi-squared test [fogarty2018quantitative 176]
Multiple linear regression with OLS [fogarty2018quantitative 192ff]

<!-- TC:ignore -->
```{r echo = FALSE, results='asis'}
sampling_table_categorical()
sampling_table_numerical()
```
<!-- TC:endignore -->

## Dependent and Independent Variables

Levels of measurement: nominal, ordinal, interval, and ratio [@fogarty2018quantitative 56]

<!-- TC:ignore -->
```{r echo = FALSE, fig.cap="Scatterplot of Income and Sex"}
outcome_var_plot()
```
<!-- TC:endignore -->

<!--  \pagebreak -->
# Results and discussion
<!-- Word count: approx. 1300 -->
<!-- In this section your goal is to demonstrate that you can interpret quantitative results. Additional credit is available if you are able to relate these findings to social science theories or if you can put the findings in context. -->

Here comes the regression.

@@

Influential data points / outliers [fogarty2018quantitative 221-222]

## Check for Heteroscedasticity
Here comes a check for heteroscedasticity.

<!-- TC:ignore -->
```{r echo = FALSE, fig.cap="Scatterplot of Fitted Values and Residuals"}
hetero_plot()
#model2 <-coeftest(model, vcov = vcovHC)
```
<!-- TC:endignore -->

## Reliability and Validity

Reliability and validity [@bryman2016social 41]
Internal and external validity [@bryman2016social 41-42]

<!-- \pagebreak -->
# Conclusion
<!-- Word count: approx. 500 -->
<!-- Clearly state your findings. Do the findings raise any questions for future research? -->

@@

>>>>

---
title: 'More than Likes: A bla bla of bla bla with bla bla'
subtitle: |
  | 
  | University of Copenhagen
  | `r source("scripts/utils.R")`
  | Student IDs:
  | XXXxxx
  | XXXxxx
  | Master's Thesis
  | Number of characters: xxxxxxxxx
  | `r # maybe for word count: RmdWords("paper.Rmd")$num_words`
output:
  pdf_document:
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: yes
  html_document: 
    number_sections: yes
    toc: true
    toc_depth: 2
header-includes:
- \usepackage{amsmath} # format math stuff
- \usepackage{booktabs} # makes table nicer
- \usepackage{lastpage} # be able to count total pages
- \usepackage{fancyhdr} # header/footer
- \pagestyle{fancy} # header/footer
- \fancyhead{} # remove header
- \renewcommand{\headrulewidth}{0pt} # remove header
- \fancyfoot[CO,CE]{Page \thepage\ of \pageref{LastPage}} # add Page X of Y
- \usepackage{floatrow} # position tables and figures correctly
- \floatsetup[figure]{capposition=top} # position tables and figures correctly
- \floatsetup[table]{capposition=top} # position tables and figures correctly
- \usepackage{setspace} # controls line spacing
bibliography: references.bib # add bibliography
csl: chicago-author-date # choose chicago citation style
link-citations: yes # add links in citations
nocite: '*' # add all used citations
---

@@

# Introduction
<!-- Word count: approx. 400  -->
<!-- Word count now: 426  -->

\onehalfspacing <!-- OBS: We use double spacing here. Could also be changed to \onehalfspacing -->

\pagebreak
# Data and Method

\pagebreak 
# Results and discussion

@@

\pagebreak
# Conclusion

@@

<div id="refs"></div>

# Appendix
